Developing a preprint culture in biology

### 2012-10-17 ms.tex

\documentclass[letterpaper,twocolumn,superscriptaddress,showkeys,longbibliography]{revtex4-1}
\usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\hypersetup
{
    colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}

@@

Public preprint servers allow authors to make manuscripts publicly available
before, or in parallel to, submitting them to journals for traditional
peer-review. The rationale for preprint servers is fundamentally simple: to make
the results of scientific research available to the scientific community as soon
as possible, instead of waiting until the peer-review process is fully
completed.  Sharing manuscripts using preprint servers has numerous advantages
including: 1) rapid dissemination of work-in-progress to a wider audience; 2)
improved peer review by encouraging feedback from the entire research community;
and 3) a fair and straightforward way to establish precedence.

@@

Posting manuscripts as preprints also has the potential to result in higher
quality science, by allowing for pre-publication feedback from a large pool of
reviewers. Prepublication reviews by a small network of colleagues are common in
the biological sciences and are an important part of the scientific process.
These "friendly" reviews increases the chances of errors being caught prior to
publication. Furthermore, the formal peer-review process as a whole is
critically over-loaded. As the number of active scientists increases and the
pressure to publish increases, it has become increasingly difficult for journals
to find reviewers \cite{hoc09}.  At the same time, rejection rates are high in
most journals \cite{aar08,roh09}, and when not invited to submit a revision,
authors must start the process over again at another journal. As a result,
initiatives to reduce time from submission to publication have emerged across
the scientific community. Rohr et al.  \cite{roh09} called for the recycling and
reuse of peer-reviews: by attaching previous reviews and detailed replies to a
new submission, both the editor and the referees can gauge the work done on the
manuscript, and perhaps evaluate it with less prejudice. A widespread use of
preprint servers can achieve the same goal of reducing the time spent in review.
With a rich enough community of scientists depositing preprints, and commenting
on them, the process of an open pre-review can become widespread and will
overall increase the quality of first submissions \cite{hoc12}.

@@

\begin{table*}
    \centering
    \begin{tabular}{|ll|}
    \hline
    Publisher                                   & Policy \\
    \hline
    Springer                            	& Accept \\
    BMC                                 	& Accept \\
    Elsevier                            	& Accept \\
    Nature Publishing Group             	& Accept \\
    Public Library of Science           	& Accept \\
    Genetics Society of America                 & Accept \\
    Royal Society                       	& Accept \\
    National Academy of Science (USA)           & Accept \\
    Ecological Society of America       	& Accept \\
    Oxford Journals                             & Accept \\
    Science                             	& Ambiguous \\
    Wiley-Blackwell                       	& No general policy \\
    British Ecological Society                  & No answer to our query \\
    \hline
    \end{tabular}
    \caption{Policies for important publishers in biology. Some publishers
tolerate preprints except for a few of their medical journals, e.g.: Journal
of the National Cancer Institute from Oxford and The Lancer from Elsevier.}
    \label{table:policies}
\end{table*}

>>>>

\documentclass[letterpaper,twocolumn,superscriptaddress,showkeys,longbibliography]{revtex4}
\usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\hypersetup
{
    colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}

@@

Public preprint servers allow authors to make manuscripts publicly available
before, or in parallel to, submitting them to journals for traditional peer-
review. The rationale for preprint servers is fundamentally simple: to make
the results of scientific research available to the scientific community as
soon as possible, instead of waiting until the peer-review process is fully
completed.  Sharing manuscripts using preprint servers has numerous advantages
including: 1) rapid dissemination of work-in-progress to a wider audience; 2)
immediate visibility of the research output for early-carreer scientsits; 3)
improved peer review by encouraging feedback from the entire research
community; and 4) a fair and straightforward way to establish precedence.

@@

Public preprints can be crucial to early-career scientists. The delay before
publication is seldom compatible with the pressure to show an impressive
publication record when applying for a scholarship or a position. Increasing
the perceived value of pre-prints as close, or equal, to journal articles (a
point we discuss in the conclusion) will allow young researchers to put their
research outcome in the open, and build a reputation for themselves through
the diffusion of their work, without the fear that this work will not be
recognized by grant or job commitees. In this perspective, mixed publication
systems like experimented by F1000Research (see below) should be encouraged as
they combine the best of both worlds: contributions are initally considered
preprints, but acquire full article status after positive reviews are
received.

Posting manuscripts as preprints also has the potential to result in higher
quality science, by allowing for pre-publication feedback from a large pool of
reviewers. Prepublication reviews by a small network of colleagues are common in
the biological sciences and are an important part of the scientific process.
These ``friendly'' reviews increases the chances of errors being caught prior to
publication. Furthermore, the formal peer-review process as a whole is
critically over-loaded. As the number of active scientists increases and the
pressure to publish increases, it has become increasingly difficult for journals
to find reviewers \cite{hoc09}.  At the same time, rejection rates are high in
most journals \cite{aar08,roh09}, and when not invited to submit a revision,
authors must start the process over again at another journal. As a result,
initiatives to reduce time from submission to publication have emerged across
the scientific community. Rohr et al.  \cite{roh09} called for the recycling and
reuse of peer-reviews: by attaching previous reviews and detailed replies to a
new submission, both the editor and the referees can gauge the work done on the
manuscript, and perhaps evaluate it with less prejudice. A widespread use of
preprint servers can achieve the same goal of reducing the time spent in review.
With a rich enough community of scientists depositing preprints, and commenting
on them, the process of an open pre-review can become widespread and will
overall increase the quality of first submissions \cite{hoc12}.

@@

\begin{table*}
    \centering
    \begin{tabular}{|ll|}
    \hline
    Publisher                                   & Policy \\
    \hline
    Springer                            	& Accept \\
    BMC                                 	& Accept \\
    Elsevier                            	& Accept \\
    Nature Publishing Group             	& Accept \\
    Public Library of Science           	& Accept \\
    Genetics Society of America                 & Accept \\
    Royal Society                       	& Accept \\
    National Academy of Science (USA)           & Accept \\
    Ecological Society of America       	& Accept \\
    Oxford Journals                             & Accept \\
    Science                             	& Ambiguous \\
    Wiley-Blackwell                       	& No general policy \\
    British Ecological Society                  & No answer to our query \\
    \hline
    \end{tabular}
    \caption{Policies for important publishers in biology. Some publishers
tolerate preprints except for a few of their medical journals, e.g.: Journal
of the National Cancer Institute from Oxford and The Lancet from Elsevier.}
    \label{table:policies}
\end{table*}
